Paper Figures

### 2019-10-03 PaperFigures.Rmd
change figure sizes/labeling

```{r plot functions}
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/tryna function.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/pvals_TB-SM.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/plot_functions.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/comp_hc_ltbi.R")

baseplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ theme(legend.position="none")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    theme(text = element_text(size=20),
          axis.text.x = element_text(size = 16),
          strip.text = element_text(size = 20))+
    theme(plot.title = element_text(hjust = 0.5, size=20)) +
    labs(x="", y="")
}

booleanplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=20), 
          axis.text.x = element_text(size=16), 
          strip.text = element_text(size = 20))+
    theme(plot.title = element_text(hjust = 0.5, size=20)) +
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10)+
    labs(x="", y="")
}

allplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=disease))+
    geom_boxplot(size=1, position=position_dodge2(width=0.2, padding = 0.2, preserve = "single"), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none") +
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    facet_wrap(~variable)+
    theme(text = element_text(size=20),
            axis.text.x = element_text(size = 16),
            strip.text = element_text(size = 20))+
    theme(plot.title = element_text(hjust = 0.5, size=20))+
    labs(x="", y="")
}

cyt_groups <- as_labeller(c("IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4", "IL13" = "IL-13"))

all_comps<-list(c("HC SM+", "HC SM-"),c("LTBI SM+", "LTBI SM-"), c("TB SM+", "TB SM-"))

healthy.cols<- c("SM+" = "#1a9850", "SM-" ="#91cf60")
ltbi.cols<- c("SM+" = "#2166ac", "SM-" = "#85ABD1")
tb.cols<- c("SM+" = "#b2182b", "SM-"="#E59EA6")
all.cols<- c("Naive" = "#C8D0D8","HC SM+" = "#1a9850", "HC SM-" ="#91cf60",
             "LTBI SM+" = "#2166ac", "LTBI SM-" = "#85ABD1",
             "TB SM+" = "#b2182b", "TB SM-"="#E59EA6")
```

@@

pval<-c(A$`SM-.HC`$p.value, A$`SM+.HC`$p.value,
        A$`SM-.LTBI`$p.value, A$`SM+.LTBI`$p.value, 
        A$`SM-.TB`$p.value, A$`SM+.TB`$p.value)
group<-c("HC SM-", "HC SM+", "LTBI SM-", "LTBI SM+", "TB SM-", "TB SM+")
table<-data.frame(cbind(group, pval))
table$pval<-as.numeric(as.character(table$pval))
table$pval[table$pval<.0001]<-"<0.0001"
kable(table, caption="TH1 to TH2")
```

some stats comparing th1 to th1/2 for reference. 
```{r}
x<-filter(plot_filter(melt), variable!="TH2.Freq")
y<-split(x,list(x$SM, x$TB)) 
A<-lapply(y, function(g) wilcox.test(value~variable, g))

pval<-c(A$`SM-.HC`$p.value, A$`SM+.HC`$p.value,
        A$`SM-.LTBI`$p.value, A$`SM+.LTBI`$p.value, 
        A$`SM-.TB`$p.value, A$`SM+.TB`$p.value)
group<-c("HC SM-", "HC SM+", "LTBI SM-", "LTBI SM+", "TB SM-", "TB SM+")
table<-data.frame(cbind(group, pval))
table$pval<-as.numeric(as.character(table$pval))
table$pval[table$pval<.0001]<-"<0.0001"
kable(table, caption="TH1 to TH1/2")
```

@@

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "disease", "value", tb.cols)+ 
    facet_wrap(~variable, labeller = cyt_groups)+
    coord_cartesian(ylim=c(0,.02))
```

@@

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
one<-baseplot(melt, "disease", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = groups, ncol=2)+
    labs(y="(%) Proliferating\nMtb-Specific CD4 T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4"))
two<-baseplot(melt, "disease", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = groups)
```

@@

a<-baseplot(melt[melt$variable=="TNFα",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,1500))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
b<-baseplot(melt[melt$variable=="IFNγ",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,18000))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
c<-baseplot(melt[melt$variable=="IL-21",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,60))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
d<-baseplot(melt[melt$variable=="IL-17A",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,20))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
e<-baseplot(melt[melt$variable=="IL-22",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,40))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
f<-baseplot(melt[melt$variable=="IL-10",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,20))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
g<-baseplot(melt[melt$variable=="IL-4",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,40))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
h<-baseplot(melt[melt$variable=="IL-5",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,15))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
i<-baseplot(melt[melt$variable=="IL-13",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,400))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))

@@

#Exporting Data
```{r}
setwd("/Users/tarynam/Desktop/Manuscript1")

>>>>

```{r plot functions}
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/tryna function.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/pvals_TB-SM.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/plot_functions.R")
source("/Users/tarynam/Desktop/Miscellaneous-Scripts/comp_hc_ltbi.R")
```

@@

x<-filter(plot_filter(melt), variable!="TH2.Freq")
y<-split(x,list(x$SM, x$TB)) 
B<-lapply(y, function(g) wilcox.test(value~variable, g))

hc<-c(A$`SM-.HC`$p.value, A$`SM+.HC`$p.value,
      B$`SM-.HC`$p.value, B$`SM+.HC`$p.value)

ltbi<-c(A$`SM-.LTBI`$p.value, A$`SM+.LTBI`$p.value, 
        B$`SM-.LTBI`$p.value, B$`SM+.LTBI`$p.value)

tb<-c(A$`SM-.TB`$p.value, A$`SM+.TB`$p.value,
      B$`SM-.TB`$p.value, B$`SM+.TB`$p.value)

label<-c("SM- TH1 to TH1/2", "SM- TH1 to TH2", "SM+ TH1 to TH1/2", "SM+ TH1 to TH2")

hc.tab<-data.frame(cbind(label, hc, p.adjust(hc, method="bonferroni")))
names(hc.tab)<-c("Comparison", "P-value", "Bonferroni Adjust P-val")
kable(hc.tab, caption="HC")

ltbi.tab<-data.frame(cbind(label, ltbi, p.adjust(ltbi, method="bonferroni")))
names(hc.tab)<-c("Comparison", "P-value", "Bonferroni Adjust P-val")
kable(ltbi.tab, caption="LTBI")

tb.tab<-data.frame(cbind(label, tb, p.adjust(tb, method="bonferroni")))
names(hc.tab)<-c("Comparison", "P-value", "Bonferroni Adjust P-val")
kable(tb.tab, caption="TB")
```

@@

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "SM", "value", tb.cols)+ 
    facet_wrap(~variable, labeller = cyt_groups)+
    coord_cartesian(ylim=c(0,.02))
```

@@

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
one<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = groups, ncol=2)+
    labs(y="(%) Proliferating\nMtb-Specific CD4 T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4"))
two<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = groups)
```

@@

a<-baseplot(melt[melt$variable=="TNFα",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,1500))+
    labs(y="pg/mL")
b<-baseplot(melt[melt$variable=="IFNγ",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,18000))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
c<-baseplot(melt[melt$variable=="IL-21",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,60))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
d<-baseplot(melt[melt$variable=="IL-17A",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,20))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
e<-baseplot(melt[melt$variable=="IL-22",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,40))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
f<-baseplot(melt[melt$variable=="IL-10",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,20))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
g<-baseplot(melt[melt$variable=="IL-4",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,40))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
h<-baseplot(melt[melt$variable=="IL-5",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,15))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
i<-baseplot(melt[melt$variable=="IL-13",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,400))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))

@@

#Exporting Data
```{r}
setwd("/Users/tarynam/Desktop/Manuscript1/figures")
cowplot::save_plot("figure8.png", lumplot, base_height=6, base_width=18)
